\cvsection{Work Experience}
\begin{cventries}
  \excventry
  {Student Developer, with Open Printing, under The Linux Foundation}
  {Google Summer Of Code}
  {WFH}
  {May 2020 - Present}
  {
    \begin{cvitems}
      \item Working on Qt Print Support to integrate the features of \textbf{Common Print Dialog Backends (CPDB)} in Qt.
      \item Ensured \textbf{abstraction} by implementing new code for the existing headers of Qt and respecting the established API.
      \item Added an entirely new functionality into the humongous code base while maintaining \textbf{binary compatibility}.
      \item Also fixed bugs in other printing libraries like the CUPS backend and  system-config-printer.
    \end{cvitems}
  }

  \excventry
  {Student Research Associate, under Prof. Sandeep K. Shukla}
  {National Interdisciplinary Center for Cyber Security and Cyber Defense of Critical Infrastructures}
  {IIT Kanpur}
  {December 2019 - Present}
  {
    \begin{cvitems}
      \item Building a tool to assess and demonstrate the interaction of attackers with a \textbf{honeypot} network.
      \item Working on the automation of the orchestration of the \textbf{Kubernetes} cluster employed for keeping the attackers engaged.
      \item Responsible for deploying new pods \textbf{in real time} as per the attack vector obtained by analysing the received payloads.
      \item Also involved in Vulnerability Assessment and Penetration Testing (\textbf{VAPT}) activities for finding new \textbf{CVE}s.
      \item Member of the organizing team of the \textbf{ScadaCTF} (a CTF on Industrial Control Systems) at Nullcon 2020 in Goa.
    \end{cvitems}
  }

  \excventry
  {Backend Developer (Summer Intern), under Prof. Manindra Agrawal}
  {New York Office, IIT Kanpur}
  {India}
  {June 2019 - August 2019}
  {
    \begin{cvitems}
      \item Worked on a scalable web application for a social network, involving a highly extensive technology stack.
      \item Built an independently-running URL shortening \textbf{microservice} that communicates with the main application using \textbf{gRPC}.
      \item Ideated and developed an entire scalable private messaging feature that uses \textbf{ScyllaDB} for quick storage of messages.
      \item Also created REST APIs on the \textbf{gorilla/mux} framework to perform CRUD operations on a \textbf{cockroach} database.
      \item Worked on a customized deployment pipeline, using arcanist and \textbf{Phabricator} for code-review.
    \end{cvitems}
  }

  \excventry
  {Student Research Associate, under Prof. Arnab Bhattacharya}
  {New Office Automation, DOIP}
  {IIT Kanpur, India}
  {December 2018}
  {
    \begin{cvitems}
      \item Found major \textbf{security flaws} in Pingala (IITK's campus automation portal), and reported them to the relevant authorities.
      \item Thereafter officially inducted into the project, and performed a \textbf{vulnerability assessment} of Pingala.
      \item Discovered multiple ways to gain unauthorized access to data, and suggested effective ways to fix them.
      \item Also implemented a modified version of the \textbf{Gale-Shapeley algorithm}, in Java, to solve the problem of efficiently\\ allocating courses to students based on their preferences - by modelling it as a \textbf{stable matching problem}.
    \end{cvitems}
  }

\end{cventries}

