\cvsection{Key Projects}

\begin{cventries}
  \cventry
  {Summer Project under Programming Club}
  {IITKBucks}
  {\texttt{\href{https://github.com/dryairship/IITKBucks}{\faGithub{} dryairship/IITKBucks}}}
  {May 2020 - July 2020}
  {
    \begin{cvitems}
      \item Mentored a group of 14 students in building their own clients for a custom \textbf{blockchain based cryptocurrency}.
      \item Taught mentees about the basics of blockchains, decentralization, digital signatures, proof-of-work, and related topics. 
      \item Resolved problems in mentees' implementations, which spanned across languages like Java, Javascript and python.
      \item Developed my own client in \textbf{Go}. Also wrote tests using the \texttt{go test} module for better code reliability.
    \end{cvitems}
  }
  
  \cventry
  {Project Track - ESC101A, under Prof. Swaprava Nath}
  {Online Election Manager}
  {\texttt{\href{https://github.com/dryairship/online-election-manager}{\faGithub{} dryairship/online-election-manager}}}
  {February 2019 - April 2019}
  {
    \begin{cvitems}
      \item Built a \textbf{cryptographically secure} online voting system to store three levels of preferences for a voter.
      \item Implemented secure and \textbf{anonymous} vote storage through a triple encryption mechanism using \textbf{ElGamal} key pairs.
      \item The system can \textbf{prove} to a voter that their vote was counted correctly, while maintaining their anonymity.
      \item \textbf{Deployed} on \texttt{elections.pclub.in}, and used for Students' Senate elections, introducing online voting for the first time.
      \item Technologies used: \textbf{Go}, \textbf{MongoDB}, \textbf{React.js}
    \end{cvitems}
  }

  \cventry
  {CSE@IITK Summer Of Code 2019, affiliated with Nutanix}
  {Smart Purchase App}
  {\texttt{\href{https://github.com/dryairship/SRATRC-Smart-Purchase-Web-App}{\faGithub{} dryairship/SRATRC-Smart-Purchase-Web-App}}}
  {May 2019 - July 2019}
  {
    \begin{cvitems}
      \item Led a team of 5 students in building a \textbf{MERN stack} web app for efficient inventory management.
      \item Built to be used by the NGO \href{https://vitraagvigyaan.org}{Vitraag Vigyaan} for  inventory and finance tracking across all their departments.
      \item Used local storage for \textbf{data caching} to reduce network usage, thereby enabling the app to work in rural areas.
    \end{cvitems}
  }
  
  \cventry
  {Facebook Hackathon: Messaging}
  {QuizKitty}
  {\texttt{\href{https://github.com/dryairship/quiz-kitty}{\faGithub{} dryairship/quiz-kitty}}}
  {May 2020 - June 2020}
  {
    \begin{cvitems}
      \item Developed a cat-themed \textbf{messenger bot} that can act as a quizmaster, using questions from an open source database.
      \item Integrated with the Messenger platform using a \textbf{webhook}, and used \textbf{Facebook Graph API} to send messages,.
      \item \textbf{Deployed} on Heroku, and available to chat on Facebook Messenger at \texttt{\href{https://m.me/quizkitty}{https://m.me/quizkitty}}.
    \end{cvitems}
  }
\end{cventries}
\vspace{-2mm}
