\section*{\sc Work Experience}
\vspace{-2mm}
\hrulefill
\vspace{1mm}

\excventry
{Google Summer of Code}
{May 2020 - Present}
{Student Developer, with OpenPrinting, under The Linux Foundation}
{
  \begin{itemize}
    \item Working on the huge code base of \textbf{Qt Print Support} to integrate the features of Common Print Dialog Backends.
    \item Ensured \textbf{abstraction} and \textbf{binary compatibility} of the library while adding an entirely new functionality into it.
    \item Also fixed bugs in other printing libraries like the CUPS backend and system-config-printer.
  \end{itemize}
}

\excventry
{National Interdisciplinary Center for Cyber Security and Cyber Defence of Critical Infrastructures}
{Dec. 2019 - Present}
{Student Research Associate, under Prof. Sandeep K. Shukla}
{
  \begin{itemize}
    \item Building tools to aid in the research on \textbf{honeypots}.
    \item Automating the orchestration of the \textbf{Kubernetes} cluster that is used as bait for fooling and engaging the attackers.
    \item Responsible for deploying pods \textbf{in real time} as per the\\attack vector obtained by analysing the received payloads.
    \item Also involved in \textbf{VAPT} activities for finding new \textbf{CVE}s.
    \item Helped organise a CTF on \textbf{SCADA ICS} at Nullcon 2020.
  \end{itemize}
}

\excventry
{New York Office, IIT Kanpur}
{June - August 2019}
{Backend Developer (Intern), under Prof. Manindra Agarwal}
{
  \begin{itemize}
    \item Worked on a large web app with an extensive tech stack.
    \item Ideated and developed an entire scalable private messaging feature that uses \textbf{ScyllaDB} for quick storage of messages.
    \item Built an independently-running URL shortening \textbf{microservice} which can be accessed through its \textbf{gRPC} server.
    \item Created REST APIs on the \textbf{gorilla/mux} framework to perform CRUD operations on a \textbf{cockroach} database.
    \item Worked on a customized deployment pipeline, using\\ arcanist and \textbf{Phabricator} for code-review.
  \end{itemize}
}

\excventry
{New Office Automation, DOIP}
{December 2018}
{Student Research Associate, under Prof. Arnab Bhattacharya}
{
  \begin{itemize}
    \item Found and reported major \textbf{security} flaws in Pingala.
    \item Thereafter officially inducted into the project, and performed a \textbf{vulnerability assessment} of the platform.
    \item Discovered multiple ways to gain unauthorized access\\to data, and suggested effective ways to resolve them.
    \item Implemented a modified version of the \textbf{Gale-Shapeley}\\\textbf{algorithm}, in Java, to efficiently allocate courses to\\ the students based on their preferences.
  \end{itemize}
}

\vspace{-2mm}