\section*{\sc Key Projects}
\vspace{-2mm}
\hrulefill
\vspace{1mm}

\cventry
{IITKBucks}
{Programming Club Summer Project}
{\href{https://github.com/dryairship/IITKBucks}{\faGithub{} dryairship/IITKBucks}}
{May - July 2020}
{
  \begin{itemize}
  \item Mentored a group of 14 students in building their own clients for a custom \textbf{blockchain based cryptocurrency}, spanning across languages like Java, Javascript and python.
  \item Taught mentees about the basics of blockchains, decentralization, digital signatures, proof-of-work, and related topics.
  \item Developed my own client in \textbf{Go} and also wrote tests for it.
  \end{itemize}
}

\cventry
{Online Election Manager}
{Project Track, ESC101A}
{\href{https://github.com/dryairship/online-election-manager}{\faGithub{} dryairship/online-election-manager}}
{February - April 2019}
{
  \begin{itemize}
  \item Built a \textbf{cryptographically secure} online voting system.
  \item Implemented secure and \textbf{anonymous} vote storage through a triple encryption mechanism using \textbf{ElGamal} key pairs.
  \item The system can \textbf{prove} the validity of the votes and results.
  \item \textbf{Deployed} and used for IITK Students' Senate Elections.
  \end{itemize}
}

\cventry
{Smart Purchase App}
{CSE@IITK Summer of Code}
{
  \href{https://github.com/dryairship/SRATRC-Smart-Purchase-Web-App}{\faGithub{} dryairship/SRATRC-Smart-Purchase-Web-App}
}
{May - July 2019}
{
  \begin{itemize}
  \item Led a team of 5 students in developing a \textbf{MERN stack} web app for inventory management and finance tracking.
  \item Used local storage for \textbf{data caching} to reduce network\\usage, thereby enabling the app to work in rural areas.
  \item Built to be used by the \textbf{NGO Vitraag Vigyaan}.
  \end{itemize}
}

\cventry
{QuizKitty}
{Facebook Hackathon: Messaging}
{
  \href{https://github.com/dryairship/quiz-kitty}{\faGithub{} dryairship/quiz-kitty}
}
{May - June 2020}
{
  \begin{itemize}
  \item Developed a quizzing \textbf{messenger bot} for the competition.
  \item Used an open source trivia database to fetch the questions.
  \item Used \textbf{Facebook Graph API} to read and send messages.
  \item Integrated with the Messenger platform using a \textbf{webhook}.
  \item \textbf{Deployed} and available to chat at \href{https://m.me/quizkitty}{https://m.me/quizkitty}.
  \end{itemize}
}

\vspace{-2mm}

